Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Framework - A Plasmode simulation study

### 2024-09-03 Writeup/appendix/Appendix.RMD
writeup-update

---
title: Supplementary Content
subtitle: Challenges of Univariate Proxy Variable Screening in High-Dimensional Propensity Score Analysis - An Argument for Multivariate Approaches
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
  html_document:
    df_print: paged
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
  word_document: default
  bookdown::html_document2:
    citation_package: natbib
    df_print: paged
    fig_caption: yes
    highlight: textmate
    keep_md: yes
    number_sections: yes
    theme: lumen
bibliography: mergedbibliography.bib
biblio-style: plainnat
always_allow_html: yes
header-includes:
- \usepackage{graphicx,longtable,booktabs,here,threeparttable}
- \usepackage{float}
- \usepackage{pdfpages}
- \usepackage{setspace}\singlespacing
- \floatplacement{figure}{H}
- \floatplacement{table}{H}
- \usepackage{xcolor,lipsum}
- \usepackage{caption}
- \captionsetup[table]{labelfont=bf}
- \usepackage[round]{natbib}
- \usepackage{pdflscape}
- \usepackage{lscape}
- \usepackage{etoolbox}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{array}
  \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
  \newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
  \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
link-citations: yes
fontsize: 10pt
geometry: margin=.8in
---
\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}

@@

>>>>

---
title: Supplementary Content
subtitle: Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Framework - A Plasmode simulation study
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
  html_document:
    df_print: paged
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
  word_document: default
  bookdown::html_document2:
    citation_package: natbib
    df_print: paged
    fig_caption: yes
    highlight: textmate
    keep_md: yes
    number_sections: yes
    theme: lumen
bibliography: mergedbibliography.bib
biblio-style: plainnat
always_allow_html: yes
header-includes:
- \usepackage{graphicx,longtable,booktabs,here,threeparttable}
- \usepackage{float}
- \usepackage{pdfpages}
- \usepackage{setspace}\singlespacing
- \floatplacement{figure}{H}
- \floatplacement{table}{H}
- \usepackage{xcolor,lipsum}
- \usepackage{caption}
- \captionsetup[table]{labelfont=bf}
- \usepackage[round]{natbib}
- \usepackage{pdflscape}
- \usepackage{lscape}
- \usepackage{etoolbox}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{array}
  \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
  \newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
  \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
link-citations: yes
fontsize: 10pt
geometry: margin=.8in
---
\appendix
\counterwithin{figure}{section}
\counterwithin{table}{section}

@@

\textcolor{red}{*need to have a brief description of these figures.*}

### 2024-09-03 Writeup/manuscript.Rmd
writeup-update

title: Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Analysis
titlerunning: High-Dimensional Propensity Score

@@

# Sample for structured abstract
abstract: |
  **Purpose**: 
  **Methods:** 
  **Results:** 
  **Conclusion:**

@@

@@

**True Data Generating Mechanism Used in Plasmode Simulation**: The primary goal of this study is to evaluate various variable selection methods under realistic conditions. To achieve this, we formulated the outcome data based on a specific model specification that incorporates both exposure and covariates, including investigator-specified and proxy variables. The model specification consists of three key components:

@@

@@

```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Bias Across Different Methods in hdPS Analysis", fig.align="center", fig.label="fig:bias-comparison"}
knitr::include_graphics("figures/metric_comparison_Bias.png")
```

```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Coverage Probability Across Different Methods in hdPS Analysis", fig.align="center", fig.label="fig:bias-comparison"}
knitr::include_graphics("figures/metric_comparison_Coverage.png")
```

@@

*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD. Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*

```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk. The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018. Methods are arranged by the number of variables used in the models.", fig.label="fig:comparison-plot", message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

@@

@@

*Report computing time for the Real-world analysis for each method. (add ordered table)*

@@

**Contextualizing the literature**:

**Summary of the simulation findings**:

**Data analysis findings**:

**Future Direction**:

**Conclusion**:

>>>>

title: Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Framework - A Plasmode simulation study
titlerunning: High-Dimensional Propensity Score

@@

# Sample for structured abstract
abstract: |
  **Purpose**: We aims to evaluate various proxy selection methods within the context of high-dimensional propensity score (hdPS) analysis. The study focuses on assessing the performance of these methods, including alternative variable selection approaches, in selecting proxy variables for confounding adjustment compared to the traditional hdPS method that is rooted in Bross formula. The goal is to understand better the performance of these alternative methods in estimating treatment effects, and identify scenarios in which they may perform better.
  **Methods:** Using data from three cycles of the National Health and Nutrition Examination Survey (NHANES) spanning 2013-2018, we motivated the study by examining the association between obesity and diabetes. A plasmode simulation framework based on this data was employed to mimic real-world data structures. Simulations were conducted under three scenarios: Frequent Exposure and Outcome, Rare Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome. The performance of a variety of proxy selection methods—including tree-based methods, LASSO-based methods, and the Genetic Algorithm (GA)—was evaluated across these scenarios using standard simulation metrics.
  **Results:** XGBoost consistently demonstrated the lowest MSE and high coverage, making it a reliable method overall, although it did not always exhibit the lowest bias. In contrast, GA consistently showed the highest bias and MSE, with lower coverage and greater variability, indicating its unsuitability for accurate effect estimation. The kitchen sink model, Bross-based hdPS, and Hybrid hdPS methods performed moderately well, with low bias and moderate MSE, but varied in coverage across scenarios. Scenario-specific trends revealed that rare outcome scenarios yielded lower MSE and better precision, while rare exposure scenarios were associated with higher bias and MSE.
  **Conclusion:** Aside from GA, the performance of most other methods in your study appears to be comparable in each scenario, though with some variations depending on specific metrics. The findings underscore the importance of selecting appropriate methods for hdPS analysis based on the characteristics of the data, particularly the prevalence of exposure and outcome. While XGBoost excelled in overall accuracy and precision, the choice of method should be tailored to the specific epidemiological goal to optimize bias, coverage, and precision in estimating treatment effects.

@@

\textcolor{red}{*need to write what hdps is, and why alternatives are considered*}

@@

**True Data Generating Mechanism Used in Plasmode Simulation**: The primary goal of this study is to evaluate various variable selection methods under realistic conditions. To achieve this, we formulated the outcome data based on a specific model specification that incorporates both exposure and covariates, including investigator-specified and proxy variables. The model specification consists of three key components (See Appendices \S A and B for further details):

@@

\textcolor{red}{*check if the description of the methods look okay to you. Make sure the description matches with the analysis codes.*}

@@

\textcolor{red}{*Can you check the app in the doc folder of the repo, and compare of the results description look accurate to you?*}

The results for each method under the different scenarios are summarized below. See Figures \ref{fig:bias-comparison} and \ref{fig:Coverage-comparison} for an overview of the performance in terms of bias and coverage, respectively.

(i) **Frequent Exposure and Outcome (base) scenario**:

1. *Bias*: The kitchen sink model, which includes all variables without selection, exhibited the smallest bias (0.0002). GA shows the highest bias (0.0287), indicating a substantial deviation from the true effect. Among the other methods, Bross-based hdPS (-0.0001), Hybrid hdPS (0.0016), and Elasticnet (0.0036) demonstrated low bias. XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly higher bias.

2. *Coverage*: The coverage for most methods was high, with Hybrid hdPS, Forward Selection, Backward Elimination, LASSO, and Elasticnet achieving values around 98%, indicating well-calibrated confidence intervals. However, GA had significantly lower coverage (83.8%), indicating that its confidence intervals might be too narrow or biased, potentially missing the true effect. After applying bias elimination, GA's coverage improved to 96%, which is better but still lower than other methods.

3. *Mean Squared Error (MSE)*: XGBoost achieved the lowest MSE (0.0006), reaffirming it as the most accurate method overall. GA maintained the highest MSE (0.0016), reflecting its higher bias and variability. The kitchen sink model (0.0009), Bross-based hdPS (0.0008), Hybrid hdPS (0.0008), and Elasticnet (0.0009) all had relatively similar and moderate MSE values.

4. *Standard Error (SE)*: XGBoost exhibited the lowest Empirical SE (0.0229), indicating high precision in its estimates. The kitchen sink model had the highest Empirical SE (0.0305), suggesting greater variability. Other methods, including GA (0.0274), Hybrid hdPS (0.0278), and Bross-based hdPS (0.0287), showed moderate variability. LASSO (0.0299) and Elasticnet (0.0294) had slightly higher variability. The Model-based SE followed a similar pattern, with XGBoost (0.0268) showing the lowest variability and the kitchen sink model (0.0333) the highest, indicating less precision in its estimates. See Appendix \S C for further details.

**(ii) Rare Exposure and Frequent Outcome**:

1. *Bias*: The kitchen sink model showed a relatively low bias (0.0025), while GA continued to exhibit the highest bias (0.0408), indicating a significant deviation from the true effect. XGBoost had a bias of 0.0259, which, while still higher than some other methods, was lower than GA. Other methods, such as Bross-based hdPS (0.0035), Hybrid hdPS (0.0049), and Elasticnet (0.0053), demonstrated moderate bias. Random Forest (RF) (0.0127) and Forward Selection (0.0108) had slightly higher bias but remained within an acceptable range.

2. *Coverage*: Coverage levels remained high for most methods, with XGBoost achieving the highest coverage at 96.2%, indicating well-calibrated confidence intervals despite its higher bias. The GA method had lower coverage (92.2%), suggesting that its confidence intervals might be narrower, potentially missing the true effect. Other methods such as RF, Forward Selection, Backward Elimination, and Hybrid hdPS maintained coverage values around 94-95%, suggesting adequate interval calibration. Bias-eliminated coverage for GA improved to 94.2%, but it was still slightly lower than other methods.

3. *Mean Squared Error (MSE)*: Hybrid hdPS and XGBoost both demonstrated the lowest MSE (0.0032), indicating that these methods were the most accurate in this scenario. The GA method had a higher MSE (0.0043), reflecting its substantial bias and variability. The kitchen sink model also had an MSE of 0.0043, similar to GA, while other methods like Bross-based hdPS (0.0035), RF (0.0039), and Elasticnet (0.0036) exhibited moderate MSE values, indicating reasonable accuracy.

4. *Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0507) and GA (0.0510), reflecting high precision despite their higher bias. The kitchen sink model had the highest Empirical SE (0.0656), indicating greater variability. Hybrid hdPS (0.0564), Bross-based hdPS (0.0595), and RF (0.0609) showed moderate variability. Forward Selection (0.0537) and Backward Elimination (0.0576) had lower variability compared to the kitchen sink model. In terms of Model-based SE, XGBoost (0.0531) and GA (0.0533) continued to show low variability, while the kitchen sink model had the highest Model-based SE (0.0623), indicating less precision in its estimates.

**(iii) Frequent Exposure and Rare Outcome**:

1. *Bias*: In this scenario, the kitchen sink model exhibited a moderate negative bias (-0.0093), similar to the Bross-based hdPS method (-0.0088). GA showed a significantly higher bias (0.0362), indicating a substantial deviation from the true effect. Among other methods, XGBoost demonstrated the lowest bias (-0.0061), while methods like Hybrid hdPS (-0.0082), Forward Selection (-0.0070), and Backward Elimination (-0.0070) had slightly higher but still moderate biases. Elasticnet and LASSO both had biases of -0.0079, reflecting slightly larger deviations compared to XGBoost but still within acceptable limits.

2. *Coverage*: Most methods achieved good coverage, with XGBoost, RF, and Forward Selection each achieving a coverage rate of 95.4%, indicating well-calibrated confidence intervals. The GA method, however, had slightly lower coverage (91.8%), indicating that its confidence intervals might be narrower, potentially excluding the true effect. Bross-based hdPS and the kitchen sink model had slightly lower coverage values of 93.8% and 93.4%, respectively. After accounting for bias, the bias-eliminated coverage for most methods, except GA, remained high, with values ranging from 98.4% to 99.0%, indicating that most methods effectively adjusted for bias in their coverage estimates. GA's bias-eliminated coverage was lower at 93.4%, reflecting its higher inherent bias.

3. *Mean Squared Error (MSE)*: XGBoost exhibited the lowest MSE (0.0003), indicating it as the most accurate method overall in this scenario. GA had the highest MSE (0.0040), reflecting its substantial bias and variability. The kitchen sink model (0.0005), Bross-based hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and Elasticnet (0.0005) all had relatively similar MSE values, indicating moderate accuracy.

4. *Standard Error (SE)*: The lowest Empirical SE was observed with XGBoost (0.0152), reflecting high precision in its estimates. The GA method exhibited the highest Empirical SE (0.0523), indicating greater variability and less precision. Methods like Hybrid hdPS (0.0184), Forward Selection (0.0187), and Elasticnet (0.0203) showed moderate variability, while Bross-based hdPS (0.0206) and the kitchen sink model (0.0212) had slightly higher variability. In terms of Model-based SE, XGBoost (0.0179) again showed the lowest variability, consistent with its low Empirical SE, indicating that it provided the most stable estimates. The kitchen sink model had a slightly higher Model-based SE (0.0219), indicating less precision in its estimates.

```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Bias Across Different Methods in hdPS Analysis\\label{fig:bias-comparison}", fig.align="center"}
knitr::include_graphics("figures/metric_comparison_Bias.png")
```

```{r, echo=FALSE, out.width="100%", fig.cap="Comparison of Coverage Probability Across Different Methods in hdPS Analysis\\label{fig:Coverage-comparison}", fig.align="center"}
knitr::include_graphics("figures/metric_comparison_Coverage.png")
```

@@

\textcolor{red}{*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD. Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*}

See Figure \ref{fig:comparison-plot} for the results from analyzing the NHANES (2013-2018) dataset.

```{r, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.cap="Figure presenting a comparison of Risk Differences (RD) and Odds Ratios (OR) with 95% confidence intervals for different methods used to evaluate the association between obesity and diabetes risk. The analysis is based on data from the National Health and Nutrition Examination Survey (NHANES) for the years 2013-2018. Methods are arranged by the number of variables used in the models.\\label{fig:comparison-plot}", message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

@@

\textcolor{red}{*need to think about how to best present this proxy in common table.*}

@@

\textcolor{red}{*Report computing time for the Real-world analysis for each method. (add ordered table or figure)*}

@@

## Summary of the simulation findings

**Comparison of methods**:

Across the three scenarios—Frequent Exposure and Outcome, Rare Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome—XGBoost consistently exhibited the lowest Mean Squared Error (MSE) and high coverage, making it one of the most reliable methods overall. However, XGBoost did not always have the lowest bias; in fact, methods such as the kitchen sink model, Bross-based hdPS, and Hybrid hdPS often showed lower bias. The GA, in contrast, consistently exhibited the highest bias and MSE, along with lower coverage and greater variability, indicating it was less reliable for accurate effect estimation. The kitchen sink model, while demonstrating low bias and reasonable MSE, generally had higher variability and lower precision compared to other methods like XGBoost. Methods such as Bross-based hdPS, Hybrid hdPS, and Elasticnet performed moderately well across all scenarios, balancing bias, coverage, and MSE, but they did not outperform XGBoost in overall accuracy and precision.

**Comparison of scenarios**:

Scenarios with rare exposure tended to produce higher bias, particularly for methods like GA and XGBoost, while frequent outcomes generally led to lower bias. Overcoverage was common in the frequent exposure and outcome scenario, while the other scenarios tended to have more balanced or slightly under-coverage. Frequent exposure scenarios had higher relative error, indicating more difficulty in precisely estimating effects compared to rare exposure scenarios, which had lower relative error. Rare outcome scenarios tended to have the lowest MSE, indicating more precise effect estimates under these conditions, whereas rare exposure scenarios had higher MSE, reflecting the challenges of estimating effects when exposure is uncommon.

## Contextualizing the literature

\textcolor{red}{*need to write what hdps offers in the literature; what additional selection criteria was used so far*}

## Data analysis findings

\textcolor{red}{*summarize real data analysis finding in 1 para*}

## Future Direction

\textcolor{red}{*TMLE*}

## Conclusion

In conclusion, this analysis highlights the importance of carefully selecting appropriate methods for hdPS analysis based on the specific characteristics of the data, particularly the prevalence of exposure and outcome. While XGBoost consistently demonstrated strong performance in terms of MSE and coverage, it did not always have the lowest bias, suggesting that it may be most suitable when precision is prioritized over bias minimization. GA, despite its potential, showed significant limitations with consistently high bias and MSE, making it less reliable for accurate effect estimation. The kitchen sink model, Bross-based hdPS, and Hybrid hdPS methods provided a balanced approach, often delivering low bias and moderate MSE, but with variability in coverage depending on the scenario. Scenario-specific trends revealed that rare outcomes generally yielded lower MSE and better precision, while rare exposures were associated with higher bias and MSE, emphasizing the challenges of accurately estimating effects in such contexts. Ultimately, the findings underscore the need to tailor method selection to the epidemiological scenario at hand, ensuring that the chosen approach aligns with the specific goals and challenges of the analysis.

### 2024-09-03 Writeup/manuscript.tex
writeup-update

\title[High-Dimensional Propensity Score]{Understanding the role of
different proxy selection methods in High-Dimensional Propensity Score
Analysis}

@@

\abstract{\textbf{Purpose}: \textbf{Methods:} \textbf{Results:}
\textbf{Conclusion:}}

@@

\textbf{True Data Generating Mechanism Used in Plasmode Simulation}: The
primary goal of this study is to evaluate various variable selection
methods under realistic conditions. To achieve this, we formulated the
outcome data based on a specific model specification that incorporates
both exposure and covariates, including investigator-specified and proxy
variables. The model specification consists of three key components:

@@

@@

\emph{Here we include full data analysis (with some summary results like
exposure and outcome prevalence, and sample size) and report OR and RD.
Also mention how many proxies were chosen (add in the picture of RD and
OR; side by side for each method, ordered my magnitude of RD), and how
many were in common with hdPS (add table).}

@@

\emph{Report computing time for the Real-world analysis for each method.
(add ordered table)}

@@

\textbf{Contextualizing the literature}:

\textbf{Summary of the simulation findings}:

\textbf{Data analysis findings}:

\textbf{Future Direction}:

\textbf{Conclusion}:

>>>>

\title[High-Dimensional Propensity Score]{Understanding the role of
different proxy selection methods in High-Dimensional Propensity Score
Framework - A Plasmode simulation study}

@@

\abstract{\textbf{Purpose}: We aims to evaluate various proxy selection
methods within the context of high-dimensional propensity score (hdPS)
analysis. The study focuses on assessing the performance of these
methods, including alternative variable selection approaches, in
selecting proxy variables for confounding adjustment compared to the
traditional hdPS method that is rooted in Bross formula. The goal is to
understand better the performance of these alternative methods in
estimating treatment effects, and identify scenarios in which they may
perform better. \textbf{Methods:} Using data from three cycles of the
National Health and Nutrition Examination Survey (NHANES) spanning
2013-2018, we motivated the study by examining the association between
obesity and diabetes. A plasmode simulation framework based on this data
was employed to mimic real-world data structures. Simulations were
conducted under three scenarios: Frequent Exposure and Outcome, Rare
Exposure and Frequent Outcome, and Frequent Exposure and Rare Outcome.
The performance of a variety of proxy selection methods---including
tree-based methods, LASSO-based methods, and the Genetic Algorithm
(GA)---was evaluated across these scenarios using standard simulation
metrics. \textbf{Results:} XGBoost consistently demonstrated the lowest
MSE and high coverage, making it a reliable method overall, although it
did not always exhibit the lowest bias. In contrast, GA consistently
showed the highest bias and MSE, with lower coverage and greater
variability, indicating its unsuitability for accurate effect
estimation. The kitchen sink model, Bross-based hdPS, and Hybrid hdPS
methods performed moderately well, with low bias and moderate MSE, but
varied in coverage across scenarios. Scenario-specific trends revealed
that rare outcome scenarios yielded lower MSE and better precision,
while rare exposure scenarios were associated with higher bias and MSE.
\textbf{Conclusion:} Aside from GA, the performance of most other
methods in your study appears to be comparable in each scenario, though
with some variations depending on specific metrics. The findings
underscore the importance of selecting appropriate methods for hdPS
analysis based on the characteristics of the data, particularly the
prevalence of exposure and outcome. While XGBoost excelled in overall
accuracy and precision, the choice of method should be tailored to the
specific epidemiological goal to optimize bias, coverage, and precision
in estimating treatment effects.}

@@

\textbf{True Data Generating Mechanism Used in Plasmode Simulation}: The
primary goal of this study is to evaluate various variable selection
methods under realistic conditions. To achieve this, we formulated the
outcome data based on a specific model specification that incorporates
both exposure and covariates, including investigator-specified and proxy
variables. The model specification consists of three key components (See
Appendices \S A and B for further details):

@@

\textcolor{red}{*Can you check the app in the doc folder of the repo, and compare of the results description look accurate to you?*}

The results for each method under the different scenarios are summarized
below. See Figures \ref{fig:bias-comparison} and
\ref{fig:Coverage-comparison} for an overview of the performance in
terms of bias and coverage, respectively.

\begin{enumerate}
\def\labelenumi{(\roman{enumi})}
\tightlist
\item
  \textbf{Frequent Exposure and Outcome (base) scenario}:
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Bias}: The kitchen sink model, which includes all variables
  without selection, exhibited the smallest bias (0.0002). GA shows the
  highest bias (0.0287), indicating a substantial deviation from the
  true effect. Among the other methods, Bross-based hdPS (-0.0001),
  Hybrid hdPS (0.0016), and Elasticnet (0.0036) demonstrated low bias.
  XGBoost (0.0074) and Random Forest (RF) (0.0034) still had slightly
  higher bias.
\item
  \emph{Coverage}: The coverage for most methods was high, with Hybrid
  hdPS, Forward Selection, Backward Elimination, LASSO, and Elasticnet
  achieving values around 98\%, indicating well-calibrated confidence
  intervals. However, GA had significantly lower coverage (83.8\%),
  indicating that its confidence intervals might be too narrow or
  biased, potentially missing the true effect. After applying bias
  elimination, GA's coverage improved to 96\%, which is better but still
  lower than other methods.
\item
  \emph{Mean Squared Error (MSE)}: XGBoost achieved the lowest MSE
  (0.0006), reaffirming it as the most accurate method overall. GA
  maintained the highest MSE (0.0016), reflecting its higher bias and
  variability. The kitchen sink model (0.0009), Bross-based hdPS
  (0.0008), Hybrid hdPS (0.0008), and Elasticnet (0.0009) all had
  relatively similar and moderate MSE values.
\item
  \emph{Standard Error (SE)}: XGBoost exhibited the lowest Empirical SE
  (0.0229), indicating high precision in its estimates. The kitchen sink
  model had the highest Empirical SE (0.0305), suggesting greater
  variability. Other methods, including GA (0.0274), Hybrid hdPS
  (0.0278), and Bross-based hdPS (0.0287), showed moderate variability.
  LASSO (0.0299) and Elasticnet (0.0294) had slightly higher
  variability. The Model-based SE followed a similar pattern, with
  XGBoost (0.0268) showing the lowest variability and the kitchen sink
  model (0.0333) the highest, indicating less precision in its
  estimates. See Appendix \S C for further details.
\end{enumerate}

\textbf{(ii) Rare Exposure and Frequent Outcome}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Bias}: The kitchen sink model showed a relatively low bias
  (0.0025), while GA continued to exhibit the highest bias (0.0408),
  indicating a significant deviation from the true effect. XGBoost had a
  bias of 0.0259, which, while still higher than some other methods, was
  lower than GA. Other methods, such as Bross-based hdPS (0.0035),
  Hybrid hdPS (0.0049), and Elasticnet (0.0053), demonstrated moderate
  bias. Random Forest (RF) (0.0127) and Forward Selection (0.0108) had
  slightly higher bias but remained within an acceptable range.
\item
  \emph{Coverage}: Coverage levels remained high for most methods, with
  XGBoost achieving the highest coverage at 96.2\%, indicating
  well-calibrated confidence intervals despite its higher bias. The GA
  method had lower coverage (92.2\%), suggesting that its confidence
  intervals might be narrower, potentially missing the true effect.
  Other methods such as RF, Forward Selection, Backward Elimination, and
  Hybrid hdPS maintained coverage values around 94-95\%, suggesting
  adequate interval calibration. Bias-eliminated coverage for GA
  improved to 94.2\%, but it was still slightly lower than other
  methods.
\item
  \emph{Mean Squared Error (MSE)}: Hybrid hdPS and XGBoost both
  demonstrated the lowest MSE (0.0032), indicating that these methods
  were the most accurate in this scenario. The GA method had a higher
  MSE (0.0043), reflecting its substantial bias and variability. The
  kitchen sink model also had an MSE of 0.0043, similar to GA, while
  other methods like Bross-based hdPS (0.0035), RF (0.0039), and
  Elasticnet (0.0036) exhibited moderate MSE values, indicating
  reasonable accuracy.
\item
  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
  XGBoost (0.0507) and GA (0.0510), reflecting high precision despite
  their higher bias. The kitchen sink model had the highest Empirical SE
  (0.0656), indicating greater variability. Hybrid hdPS (0.0564),
  Bross-based hdPS (0.0595), and RF (0.0609) showed moderate
  variability. Forward Selection (0.0537) and Backward Elimination
  (0.0576) had lower variability compared to the kitchen sink model. In
  terms of Model-based SE, XGBoost (0.0531) and GA (0.0533) continued to
  show low variability, while the kitchen sink model had the highest
  Model-based SE (0.0623), indicating less precision in its estimates.
\end{enumerate}

\textbf{(iii) Frequent Exposure and Rare Outcome}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Bias}: In this scenario, the kitchen sink model exhibited a
  moderate negative bias (-0.0093), similar to the Bross-based hdPS
  method (-0.0088). GA showed a significantly higher bias (0.0362),
  indicating a substantial deviation from the true effect. Among other
  methods, XGBoost demonstrated the lowest bias (-0.0061), while methods
  like Hybrid hdPS (-0.0082), Forward Selection (-0.0070), and Backward
  Elimination (-0.0070) had slightly higher but still moderate biases.
  Elasticnet and LASSO both had biases of -0.0079, reflecting slightly
  larger deviations compared to XGBoost but still within acceptable
  limits.
\item
  \emph{Coverage}: Most methods achieved good coverage, with XGBoost,
  RF, and Forward Selection each achieving a coverage rate of 95.4\%,
  indicating well-calibrated confidence intervals. The GA method,
  however, had slightly lower coverage (91.8\%), indicating that its
  confidence intervals might be narrower, potentially excluding the true
  effect. Bross-based hdPS and the kitchen sink model had slightly lower
  coverage values of 93.8\% and 93.4\%, respectively. After accounting
  for bias, the bias-eliminated coverage for most methods, except GA,
  remained high, with values ranging from 98.4\% to 99.0\%, indicating
  that most methods effectively adjusted for bias in their coverage
  estimates. GA's bias-eliminated coverage was lower at 93.4\%,
  reflecting its higher inherent bias.
\item
  \emph{Mean Squared Error (MSE)}: XGBoost exhibited the lowest MSE
  (0.0003), indicating it as the most accurate method overall in this
  scenario. GA had the highest MSE (0.0040), reflecting its substantial
  bias and variability. The kitchen sink model (0.0005), Bross-based
  hdPS (0.0005), and other methods like Hybrid hdPS (0.0004) and
  Elasticnet (0.0005) all had relatively similar MSE values, indicating
  moderate accuracy.
\item
  \emph{Standard Error (SE)}: The lowest Empirical SE was observed with
  XGBoost (0.0152), reflecting high precision in its estimates. The GA
  method exhibited the highest Empirical SE (0.0523), indicating greater
  variability and less precision. Methods like Hybrid hdPS (0.0184),
  Forward Selection (0.0187), and Elasticnet (0.0203) showed moderate
  variability, while Bross-based hdPS (0.0206) and the kitchen sink
  model (0.0212) had slightly higher variability. In terms of
  Model-based SE, XGBoost (0.0179) again showed the lowest variability,
  consistent with its low Empirical SE, indicating that it provided the
  most stable estimates. The kitchen sink model had a slightly higher
  Model-based SE (0.0219), indicating less precision in its estimates.
\end{enumerate}

@@

\textcolor{red}{*Here we include full data analysis (with some summary results like exposure and outcome prevalence, and sample size) and report OR and RD. Also mention how many proxies were chosen (add in the picture of RD and OR; side by side for each method, ordered my magnitude of RD), and how many were in common with hdPS (add table).*}

See Figure \ref{fig:comparison-plot} for the results from analyzing the
NHANES (2013-2018) dataset.

@@

\textcolor{red}{*Report computing time for the Real-world analysis for each method. (add ordered table or figure)*}

@@

\subsection{Summary of the simulation
findings}\label{summary-of-the-simulation-findings}

\textbf{Comparison of methods}:

Across the three scenarios---Frequent Exposure and Outcome, Rare
Exposure and Frequent Outcome, and Frequent Exposure and Rare
Outcome---XGBoost consistently exhibited the lowest Mean Squared Error
(MSE) and high coverage, making it one of the most reliable methods
overall. However, XGBoost did not always have the lowest bias; in fact,
methods such as the kitchen sink model, Bross-based hdPS, and Hybrid
hdPS often showed lower bias. The GA, in contrast, consistently
exhibited the highest bias and MSE, along with lower coverage and
greater variability, indicating it was less reliable for accurate effect
estimation. The kitchen sink model, while demonstrating low bias and
reasonable MSE, generally had higher variability and lower precision
compared to other methods like XGBoost. Methods such as Bross-based
hdPS, Hybrid hdPS, and Elasticnet performed moderately well across all
scenarios, balancing bias, coverage, and MSE, but they did not
outperform XGBoost in overall accuracy and precision.

\textbf{Comparison of scenarios}:

Scenarios with rare exposure tended to produce higher bias, particularly
for methods like GA and XGBoost, while frequent outcomes generally led
to lower bias. Overcoverage was common in the frequent exposure and
outcome scenario, while the other scenarios tended to have more balanced
or slightly under-coverage. Frequent exposure scenarios had higher
relative error, indicating more difficulty in precisely estimating
effects compared to rare exposure scenarios, which had lower relative
error. Rare outcome scenarios tended to have the lowest MSE, indicating
more precise effect estimates under these conditions, whereas rare
exposure scenarios had higher MSE, reflecting the challenges of
estimating effects when exposure is uncommon.

\subsection{Contextualizing the
literature}\label{contextualizing-the-literature}

\textcolor{red}{*need to write what hdps offers in the literature; what additional selection criteria was used so far*}

\subsection{Data analysis findings}\label{data-analysis-findings}

\textcolor{red}{*summarize real data analysis finding in 1 para*}

\subsection{Future Direction}\label{future-direction}

\textcolor{red}{*TMLE*}

\subsection{Conclusion}\label{conclusion}

In conclusion, this analysis highlights the importance of carefully
selecting appropriate methods for hdPS analysis based on the specific
characteristics of the data, particularly the prevalence of exposure and
outcome. While XGBoost consistently demonstrated strong performance in
terms of MSE and coverage, it did not always have the lowest bias,
suggesting that it may be most suitable when precision is prioritized
over bias minimization. GA, despite its potential, showed significant
limitations with consistently high bias and MSE, making it less reliable
for accurate effect estimation. The kitchen sink model, Bross-based
hdPS, and Hybrid hdPS methods provided a balanced approach, often
delivering low bias and moderate MSE, but with variability in coverage
depending on the scenario. Scenario-specific trends revealed that rare
outcomes generally yielded lower MSE and better precision, while rare
exposures were associated with higher bias and MSE, emphasizing the
challenges of accurately estimating effects in such contexts.
Ultimately, the findings underscore the need to tailor method selection
to the epidemiological scenario at hand, ensuring that the chosen
approach aligns with the specific goals and challenges of the analysis.
